Solar wind discontinuities spatial evolution

### 2024-01-24 index.qmd
update AGU23 poster
update
add agu pdf format

---
title: Solar wind discontinuities spatial evolution
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
bibliography: files/references.bib
execute: 
  eval: false
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
---

## Background

@@

### Importance

@@

### Motivations

@@

## Methods

@@

### ID identification (limited feature extraction / anomaly detection)

@@

### Solar Wind Model {#solar-wind-model}

@@

## Results

@@

### Occurrence rates

@@

### Properties

@@

## Conclusion

-   We have collected 5 years of solar wind discontinuities from JUNO, ARTEMIS and STEREO.
-   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
-   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-   The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
-   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.

>>>>

---
title: Solar wind discontinuities spatial evolution
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
  - name: Shi Chen
    orcid: 0000-0002-2582-7085
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
execute: 
  eval: false
code-links:
  - repo
  - href: https://app.tana.inc?nodeid=Kmdzbyj-36NM
    text: Tana
---

# Background

@@

## Importance

@@

## Motivations

@@

# Methods

@@

## ID identification (limited feature extraction / anomaly detection)

@@

## Solar Wind Model {#solar-wind-model}

@@

# Results

@@

## Occurrence rates

@@

## Properties

@@

# Conclusion

-   We have collected 5 years of solar wind discontinuities from JUNO, aMIS and STEREO.
-   We have developed a pipeline to identify solar wind discontinuities. (Modular, Performant, Scalable)
-   The normalized occurrence rate of IDs drops with the radial distance from the Sun, following $1/r$ law.
-   The thickness of IDs increases with the radial distance from the Sun, but after normalization to ion inertial length, the thickness of IDs decreases.
-   The current intensity of IDs decrease with the radial distance from the Sun, but after normalization to the Alfven current , the current intensity of IDs increases.

# Figures

::: {#fig-examples layout-nrow="1"}

![](figures/examples/artemis_id_example.png)

![](figures/examples/stereo_id_example.png)

Examples of IDs from ARTEMIS, STEREO, and JUNO

:::

<!-- ![Near-Earth' solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-omni_overview} -->

[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}

![Model validation](figures/model/juno_model_validation_full){#fig-modelValidation}

![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-tsEffect}
